Investigating the Effect of Dataset Representivity for Image Colourisation

### 2019-10-09 Paper/paper.tex
Added Sample images

\textbf{Include sample images here}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
Learning Rate & Epochs & Workers & Batch Size \\ 
\hline 
0.001 & 75 & 4 & 64 \\ 
\hline 
\end{tabular} 
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Local inclusion \% & 0\% & 10\% & 20\% & 30\%  \\ 
\hline 
Loss $\times 10^{-3}$& 2.727 & 2.696 & 2.660 & 2.638\\ 
\hline 
\end{tabular} 
\end{table}

>>>>

\begin{table}[h!]
\centering
\begin{tabular}{cc}
\includegraphics[width=3.7cm]{SampleSA/46} & \includegraphics[width=3.7cm]{SampleSA/61}\\
\includegraphics[width=3.7cm]{SampleSA/67} & \includegraphics[width=3.7cm]{SampleSA/69}\\
\includegraphics[width=3.7cm]{SampleSA/106} & \includegraphics[width=3.7cm]{SampleSA/127}\\
\caption{Sample images from the South African dataset}
\end{tabular}
\label{fig:samplesa}
\end{table}

@@

\begin{table}[h!]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|}
\hline 
Learning Rate & Epochs & Workers & Batch Size \\ 
\hline 
0.001 & 75 & 4 & 64 \\ 
\hline 
\end{tabular} 
\end{table}

@@

\begin{table}[h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|l||c|c|c|c|}
\hline 
Local inclusion \% & 0\% & 10\% & 20\% & 30\%  \\
\hline
Loss $\times 10^{-3}$& 2.727 & 2.696 & 2.660 & 2.638\\ 
\hline 
\end{tabular} 
\end{table}

As you can see, the diffrence in loss is miniscule. The small drop in loss that you get when including local data is not worth the time and effort spent retrieving, processing and preparing it in the first place. The majority of datasets used in image colourisation or classification already contain a wide variety of images that will make including local data redundant. By no means does this mean that the inclusion of local data plays no role in producing better looking images that more closely resemble the place of origin. It does, however, mean that the inclusion of local data simply does not effect the outcome of the experiment as much as other factors would. Other factors include running the experiment for longer or simply finding a larger dataset. The insignificance of local data inclusion is made extremely evident when comparing images that were produced using a model trained without any local data with a model trained using 30\% local data,

\begin{figure}[h!]
    \centering
    \subfloat[0\% inclusion]{{\includegraphics[width=3.8cm]{Inclusion_compare/0} }}%
    \qquad
    \subfloat[30\% inclusion]{{\includegraphics[width=3.8cm]{Inclusion_compare/30} }}%
    \caption{A colourised image produced using models with varying inclusion of local data}%
    \label{fig:inclusion_compare}
\end{figure}

The difference above is extremely minute. You may not even be able to see the difference but upon closer inspection, the image produced with local data contains greens that are more yellow and brighter as well as grass that is more vivid and South African. These changes may very well go unnoticed and coincide with the small changes observed in the loss value.
